---
title: "Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
shootings <- read.csv("data/shootings-2018.csv", stringsAsFactors = FALSE)
```

## Summary Information
```{r echo=FALSE}
summary <- get_summary_info(shootings)
```
> See the original dataset [here]("http://www.shootingtracker.com/")

In the United States, there have been `r summary$n_shootings` shootings. In those shootings, `r summary$n_lives_lost` lives have been lost. `r summary$most_impacted_city` was the city most impacted by these shootings, with the most casualties of any city. On average, every shooting that occurs in the US will lead to the death of `r summary$avg_death` deaths. On average, every shooting will also have `r summary$avg_injuries` injuries as well.

## Summary Table
```{r echo=FALSE}
table <- get_summary_table(shootings)
```
`r table`
From this table, we can see that Chicago has the most incidents of any city, with 135 casualties. Other cities such as Philadelphia and Memphis also suffer from a significant amount of shooting incidents, with 49 and 43 respectively. It can be drawn that many of the cities with the highest number of shooting-related casualties are among the most densely populated.

## Incident With The Most Casualties
```{r echo=FALSE}
most_casualties_info <- get_most_casualties_info(shootings)
```
The shooting with the most casualties overall was the [Douglas High School Shooting](https://www.nytimes.com/2018/02/14/us/parkland-school-shooting.html). This shooting occurred in `r most_casualties_info$city`, `r most_casualties_info$state`. This shooting occurred on `r most_casualties_info$date`. There were `r most_casualties_info$n_injured` injuries and `r most_casualties_info$n_killed` deaths.

## Interactive Map
```{r echo=FALSE}
map <- get_interactive_map(shootings)
```
`r map`
This map allows us to judge the geographical differences in where shootings occur. Here you can see clearly that the locations with the most shootings are often densely populated areas. In addition, one can also view that shootings are not localized to any one state or region -- they occur throughout many places in the United States. 

## Plot of Casualties By State
```{r echo=FALSE}
barplot <- get_bar_plot(shootings)
```
One question I had is which states would benefit the most from increased focus on shootings, and whether those states had anything in common. For that, I created this bar graph.
`r barplot`
One insight you can gain is that three states (California, Florida, Illinois) account for a large number of the shootings. Another insight is that even without those three states, the most popular states are the ones with more casualties, and the less popular ones with less casualties.