---
title: "Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
shootings <- read.csv("data/shootings-2018.csv", stringsAsFactors = FALSE)
```

## Summary Information
```{r echo=FALSE}
summary <- get_summary_info(shootings)
```
> See the original dataset [here]("http://www.shootingtracker.com/")

In the United States, there have been `r summary$n_shootings` shootings. In those shootings, `r summary$n_lives_lost` lives have been lost. `r summary$most_impacted_city` was the city most impacted by these shootings, with the most casualties of any city. On average, every shooting that occurs in the US will lead to the death of `r summary$avg_death` deaths. On average, every shooting will also have `r summary$avg_injuries` injuries as well.

## Summary Table
From this table, we can see that `max_city` has the most incidents of any city, `but not by a lot`. Other cities such as `other cities` also suffer from a significant amount of shooting incidents. `more insights here`

## Description of a Particular Incident
`find a link to a description of a particular incident`

## Interactive Map
This map allows us to judge the geographical differences in where shootings occur. Here you can see `insight one`. In addition, `insight two`.

## Custom Plot
Some analysis and scatterplot goes here.